Selection of Polynomial Features by Genetic Algorithms

### 2013-07-22 texts/paper-draft.tex
test sync

\documentclass[12pt]{article}

@@

%
%	PAGE GEOMETRY
%
\usepackage{geometry}
\geometry{a4paper}
%

@@

%
%	TIKZ AND RELATED STUFF
%
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{statistics}
%
%	avoid processing figures every time
\usepgfplotslibrary{external}
\tikzexternalize
% ENABLE NEXT LINE TO TYPESET FIGURES
\tikzset{external/force remake}
%

@@

\title{Selection of Polynomial Features by Genetic Algorithms}
\author{Francisco Coelho \and João Neto}
\date{[{\sc draft} \today]}

@@

\maketitle
\begin{abstract}
Many applications require models that have no acceptable linear approximation and many nonlinear models are defined by polynomials. The use of genetic algorithms to find polynomial models is decades old but still poses challenges due to the complexity of the search and different definitions of optimal solution.

@@

@@

\begin{figure}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
\begin{axis}[
	width=0.5\textwidth,height=6cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	title = {Abalone Dataset},
	xlabel = {Error (Abalone)},
	ylabel={Regularization ($\lambda$)},
	]	
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/figure1.dat};
	\addplot[boxplot] table [y index=2] {data/figure1.dat};
	\addplot[boxplot] table [y index=4] {data/figure1.dat};
	\addplot[boxplot] table [y index=6] {data/figure1.dat};		
	\addplot[boxplot] table [y index=8] {data/figure1.dat};
	\addplot[boxplot] table [y index=10] {data/figure1.dat};
	\addplot[boxplot] table [y index=12] {data/figure1.dat};
\end{axis}	
\end{tikzpicture}
%
% RIGHT PANE
&
%
%
\begin{tikzpicture}
\begin{axis}[
	width=0.5\textwidth,height=6cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	title = {Auto MPG Dataset},
	xlabel={Error (Auto MPG)},
	]	
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=6] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[boxplot] table [y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=12] {data/lambda.errors.Auto-Mpg.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0,
	ymax=300,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Artificial dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Articial_dataset.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Articial_dataset.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Articial_dataset.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=1] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=2] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=3] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=4] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=5] {data/Articial_dataset.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.25,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Housing dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Housing300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Housing300_lambda0.8_25runs.dat};

	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Housing300_lambda0.8_25runs.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.64,
	ymax=0.79,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Abalone dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Abalone300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Abalone300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Abalone300_lambda0.8_25runs.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.3,
	ymax=0.55,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Auto-MPG dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Auto-Mpg300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Auto-Mpg300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Auto-Mpg300_lambda0.8_25runs.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=7cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.53,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Kinematics dataset}},
	mark options={scale=0.5},
	]
	\addplot[only marks, mark=o,color=black] table [x expr=1+0.2*rand,y index=0] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=2+0.2*rand,y index=1] {data/Kinematics300_lambda0.8_25runs.dat};		
	\addplot[only marks, mark=o,color=black] table [x expr=3+0.2*rand,y index=2] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=4+0.2*rand,y index=3] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=5+0.2*rand,y index=4] {data/Kinematics300_lambda0.8_25runs.dat};
	\addplot[only marks, mark=o,color=black] table [x expr=6+0.2*rand,y index=5] {data/Kinematics300_lambda0.8_25runs.dat};

@@

\begin{axis}[
	width=0.95\textwidth,
	height=6cm,
	xmin=-5,
	xmax=255,
	mark options={scale=0.5},
	line width=1pt,
	xlabel={number of iterations},
	ylabel={\ac{rmse}},
	title={Error (\ac{rmse}) vs. number of iterations (\textbf{Abalone dataset})},
	]

@@

\section{Bibliography}

>>>>

\documentclass{elsarticle}

@@

%
%	PAGE GEOMETRY
%
%\usepackage{geometry}
%\geometry{a4paper}
%

@@

%
%	TIKZ AND RELATED STUFF
%
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{statistics}
%
%	avoid processing figures every time
\usepgfplotslibrary{external}
\tikzexternalize
% ENABLE NEXT LINE TO TYPESET FIGURES
%\tikzset{external/force remake}
%

@@

@@

\begin{frontmatter}

\title{Selection of Polynomial Features by Genetic Algorithms}
\author[ue,labmag]{Francisco Coelho}
\ead{fc@di.uevora.pt}

\author[fcul,labmag]{João Pedro Neto}
\ead{jpn@di.fc.ul.pt}

\address[ue]{Dept. Informática, Universidade de Évora, Rua Romão Ramalho 58 Évora 7000-671 Évora}
\address[fcul]{Dept. Informática, Faculdade de Ciências da Universidade de Lisboa, Campo Grande 1749-016 Lisboa}
\address[labmag]{Laboratory of Agent Modelling (LabMAg)}

\date{[{\sc draft} \today]}

\begin{abstract}
Many applications require models that have no acceptable linear approximation and many nonlinear models are defined by polynomials. The use of genetic algorithms to find polynomial models is decades old but still poses challenges due to the complexity of the search and different definitions of optimal solution.

@@

\end{frontmatter}

@@

\begin{figure}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=6cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	title = {Abalone Dataset},
	xlabel = {Error (Abalone)},
	ylabel={Regularization ($\lambda$)},
	]	
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/figure1.dat};
	\addplot[boxplot] table [y index=2] {data/figure1.dat};
	\addplot[boxplot] table [y index=4] {data/figure1.dat};
	\addplot[boxplot] table [y index=6] {data/figure1.dat};		
	\addplot[boxplot] table [y index=8] {data/figure1.dat};
	\addplot[boxplot] table [y index=10] {data/figure1.dat};
	\addplot[boxplot] table [y index=12] {data/figure1.dat};
\end{axis}	
\end{tikzpicture}
%
% RIGHT PANE
&
%
%
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=6cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	%yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	yticklabels={},
	title = {Auto MPG Dataset},
	xlabel={Error (Auto MPG)},
	]	
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=6] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[boxplot] table [y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=12] {data/lambda.errors.Auto-Mpg.dat};

@@

\begin{figure}[tb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.90\textwidth,height=6cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	yticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	ylabel={Regression Method},
	xmin=-5,
	xmax=300,
	xlabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Artificial dataset}},
	]
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=1] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=2] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=3] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=4] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=5] {data/Articial_dataset.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.98\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.25,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Housing dataset}},
	mark options={scale=0.5},
	]
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=1] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=2] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=3] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=4] {data/Housing300_lambda0.8_25runs.dat};
	\addplot[boxplot] table [y index=5] {data/Housing300_lambda0.8_25runs.dat};

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.98\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.64,
	ymax=0.79,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Abalone dataset}},
	mark options={scale=0.5},
	]

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.98\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.3,
	ymax=0.55,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Auto-MPG dataset}},
	mark options={scale=0.5},
	]

@@

\begin{figure}[htb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.98\textwidth,height=7cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6},
	xticklabels={GA.Poly,Lin.Reg,SVM,RPART,Rnd.For,CI.Tree},
	xlabel={Regression Method},
	ymin=0.53,
	ymax=0.85,
	ylabel={Error distribution (\ac{rmse})},
	title={Regression results for \textbf{Kinematics dataset}},
	mark options={scale=0.5},
	]

@@

\begin{axis}[
	width=0.98\textwidth,
	height=6cm,
	xmin=-5,
	xmax=255,
	mark options={scale=0.5},
	line width=1pt,
	xlabel={number of iterations},
	ylabel={\ac{rmse}},
	title={Error (\ac{rmse}) vs. number of iterations (\textbf{Abalone dataset})},
	]

@@

\section*{Acknowledgements}

The authors thank the Fundação para a Ciência e Tecnologia (FCT) and the  laboratório de I\&D LabMAg the financial support given to this work under the strategic project PEst-­OE/EEI/UI0434/2011.

%\section{Bibliography}
